\clearemptydoublepage

\phantomsection
\addcontentsline{toc}{chapter}{Outline of the Thesis}

\begin{center}
	\huge{Outline of the Thesis}
\end{center}

%--------------------------------------------------------------------

\noindent {\scshape Chapter 1: Introduction}  \vspace{1mm}

\noindent  The introduction describes the current challenges of securing the home, and the cost that the community hast to pay due to false positives. The motivation behind solving the problem from the perspective of smart environments is presented. Furthermore, the related work research about intrusion detection on the computer networks environment, as well as the research regarding the capabilities of current smart environments\\

\noindent {\scshape Chapter 2: Requirements Elicitation}  \vspace{1mm}

\noindent  Chapter 2 describes the requirements elicitation which includes the scenarios that drive the development of this project. Based on these scenarios, non-functional requirements are proposed and a functional model with use cases and functional requirements is elaborated. \\

\noindent {\scshape Chapter 3: Analysis}  \vspace{1mm}

\noindent  Chapter 3 describes the analysis model created to formalize the information and objects that exist in the application domain.\\

\noindent {\scshape Chapter 4: System Design}  \vspace{1mm}

\noindent  Chapter 4 describes the construction of the system design. First, the system's design goals are identified. Later, on the software architecture the system is decomposed based on their responsibility and functionality, taking into account the non-functional requirements, the models from previous chapters, and the design goals. \\

\noindent {\scshape Chapter 5: Object Design}  \vspace{1mm}

\noindent Chapter 5 describes the solution domain. In this chapter, the objects defined, pay important consideration into refining the concepts from previous chapters, as well as the objects that interact with the selected off-the-shelf components. \\
%Afterwards, the transformation of application domain objects to solution domain objects is discussed. \\

\noindent {\scshape Chapter 6: Conclusion}  \vspace{1mm}

\noindent  Chapter 6 concludes with an overview of the results. Afterwards, the results are reviewed critically and visions for future work are pointed out. \\
			
